25-Figure3-051821

### 2021-09-17 notebooks/03-Fig3abde_4acd-051821.Rmd
notebook03 changed colors and figure sizes

```{r}
sensors_pcc<- sensors_pcc%>%
    mutate(sensor_cluster=factor(replace_na(as.character(sensor_cluster),"Unclustered")),
    sensor_cluster = fct_reorder(sensor_cluster, sens))%>%
    group_by(sensor_cluster)%>%
    mutate(gid = cur_group_id())%>%ungroup()%>%
    mutate(cluster_or_go = ifelse(sensor_cluster=='Unclustered','Unclustered',
                                  ifelse(is.na(as.character(go_group)), gid, as.character(go_group))))%>%
    mutate(cluster_or_go = fct_recode(as.factor(cluster_or_go), `Iron ion\ntransport`  = "cellular response to iron ion starvation",
`Mitochondria nucleus\nsignaling pathway`="mitochondria-nucleus signaling pathway",
`Phenylalanine\ntransport`="phenylalanine transport",
`Hexose metabolic\nprocess`="hexose metabolic process",
`Tricarboxylic acid\ncycle`="tricarboxylic acid cycle"))%>%
    mutate(label = as.factor(case_when(
        cluster_or_go == 'Unclustered' ~ 'Unclustered',
        is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
        TRUE ~ paste0('SC',gid-1,'\n(',cluster_or_go,')')
    )))
```

@@

#sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sens_deg_comp <- ggplot(sensors_pcc %>% right_join(pcc_df)%>% 
                        mutate(label = factor(replace_na(as.character(label),"Non-sensor genes")),
                               label=fct_reorder(label, sens),
                               label=fct_relevel(label,'Non-sensor genes',after=Inf)), 
                        aes(x = as.factor(label), y = deg, fill = as.factor(label))) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:10],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(), 
        legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
sens_sens_comp <- ggplot(sensors_pcc %>% mutate(label = fct_reorder(label, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = (label), y = sens_norm, fill =(label))) +
  geom_boxplot() +
  geom_signif(
    comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0055, 0.0075)#, 0.008)
  ) +
  xlab("") +
  ylab("Sensitivity (a.u.)") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(),
        legend.title = element_blank())+
        ylim(NA, 0.008)

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3,height=3)

>>>>

```{r}
sensors_pcc<- sensors_pcc%>%
    mutate(sensor_cluster=factor(replace_na(as.character(sensor_cluster),"Unclustered")),
    sensor_cluster = fct_reorder(sensor_cluster, sens))%>%
    group_by(sensor_cluster)%>%
    mutate(gid = cur_group_id())%>%ungroup()%>%
    mutate(cluster_or_go = ifelse(sensor_cluster=='Unclustered','Unclustered',
                                  ifelse(is.na(as.character(go_group)), gid, as.character(go_group))))%>%
    mutate(cluster_or_go = fct_recode(as.factor(cluster_or_go), `Iron ion\ntransport`  = "cellular response to iron ion starvation",
`Mitochondria nucleus\nsignaling pathway`="mitochondria-nucleus signaling pathway",
`Phenylalanine\ntransport`="phenylalanine transport",
`Hexose metabolic\nprocess`="hexose metabolic process",
`Tricarboxylic acid\ncycle`="tricarboxylic acid cycle"))%>%
    mutate(label = as.factor(case_when(
        cluster_or_go == 'Unclustered' ~ '\nUnclustered',
       # is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
        TRUE ~ paste0('SC',gid-1)
    )))
```

@@

#sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sens_deg_comp <- ggplot(sensors_pcc %>% right_join(pcc_df)%>% 
                        mutate(label = factor(replace_na(as.character(label),"\nNon-sensor\ngenes")),
                               label=fct_reorder(label, sens),
                               label=fct_relevel(label,'\nNon-sensor\ngenes',after=Inf)), 
                        aes(x = as.factor(label), y = deg, fill = as.factor(label))) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:10],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3, size=3, vjust = 1.5) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=7), 
        legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
sens_sens_comp <- ggplot(sensors_pcc %>% mutate(label = fct_reorder(label, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = (label), y = sens_norm, fill =(label))) +
  geom_boxplot() +
  geom_signif(
    comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0058, 0.0078),
                                           textsize = 3#, 0.008)
  ) +
  xlab("") +
  ylab("Sensitivity (a.u.)") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=7),
        legend.title = element_blank())+
        ylim(NA, 0.008)

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)
